\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-11-06 jss/article.tex
edit

where $m$ is the number of regression coefficients. As for $\beta$, the flat non-informative distribution above is a common choice. In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}. In the other two cases, Poisson and Binomial, the distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian. We will show the efficiency of this assignment  in the examples in section 5.

>>>>

where $m$ is the number of regression coefficients. As for $\beta$, the flat non-informative distribution above is a common choice. In the Gaussian case, the flat prior distribution on the second-level variance $A$ is chosen to produce good repeated sampling properties for point and interval estimates of random effects $\{\mu_{j}\}$, and to have its posterior propriety when $k\ge m+3$ \citep{2011}. 
\\

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$) has a full rank ($rank(X)=m$). The Poisson model, however, can have such posterior propriety if there are two groups whose observed values are greater than 0 and the second-level mean ($\lambda_0$) is known. The efficiency of these priors is explored in the examples in section 5.
